---
title: "Lab 00 - Hello IDS!"
author: "Charlotte Senior"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Connie", "Elise", "Shona", 
           "Izzy", "Charlie"),
  github_username = c("constanceherrod", "elisehoward19", "ShonaLaird", 
                      "ishildur", "charlottesenior"), 
  colour = c("green", "blue", "blue", 
             "red", "navy blue"),
  hobby = c("netball", "crochet", "flute", 
            "basketball", "musical theater"),
  favourite_number = c(3, 9, 4, 7, 4)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


This graph shows the github username mapped against the favorite number associated with the person with that github username. It also shows each users favorite color in the bar chart.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "github username", 
          y = "favourite number",
          title = "Favourite number and colour chart")
```

I think the labs command modifies labels on axes of charts and their titles.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Maybe a pie chart would be more suitable as the bar chart would become very long and take up a lot of space on the page. However if alot of students have different hobbies the 'slices' in the pie chart may be quite small and not very readable. Still I think this is a good option.
